---
title: "Maximization"
author: "Quota baskets"
date: "1/15/2021"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

**This Rmd summarizes the meeting 01/15/2021 with Chris and Nathan. **

### Abstract

1. We set the problem of quota basket for 3 species, 3 technologies and 2 QB constraints. 

2. We agree to evaluate the maximization of the problem and consider the lambdas as given.

3. It is the first to generalize the problem.

### Set Parameters
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=F, warning=F)

# Packages
library(tidyverse)
library(Matrix)
library(kableExtra)
library(ggplot2)
library(plotly)
library(lpSolve)
library(lpSolveAPI)
library(ggpubr)
library(tinytex)
```

```{r} 
# First, set seed to ensure we have the same result 
set.seed(666)


# set the number of species and technologies we want to study
species_num <- 3
tech_num <- 3


# set the number of years we want to model the stock dynamic 
year = 3

# set the discount rate
delta = 0.05
rho = 1/(1+delta)


# set parameters
species <- c(1:species_num)
parameter <- data.frame(species)
parameter$r <- c(1,1,1)
parameter$K <- c(1,1,1)
parameter$X0 <- c(0.5,0.5,0.5)
parameter$p <- c(200,200,200)
parameter$delta <- c(0.05,0.05,0.05)
parameter$rho <- 1/(1+parameter$delta)

# set catchability coefficient 
coefficient <- c(0.05,0.04,0.04,
                 0.04,0.05,0.04,
                 0.04,0.04,0.05)
q_matrix <- matrix(coefficient, nrow = tech_num, ncol = species_num, byrow=T)

# set effort for each tech 
E <- c(0.5,0.5,0.5)

# set cost for each tech
C <- c(1,1,1)
```

We will keep our model simple. We created a model of `r tech_num` technologies and `r species_num` species for a study period of `r year` years. The price of fish depends on species (we will add in more attributes later).

```{r}
# print the parameter table
par <- kbl(parameter, caption = "Species Parameters") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
par
```

```{r}
# q_matrix <- matrix(coefficient, nrow = tech_num, ncol = species_num)
species_tech_matrix <- data.frame(q_matrix)

# assign column and row names to the matrix
matrix_col_name <-  paste("species", 1:species_num, sep = " ")
colnames(species_tech_matrix) <- matrix_col_name
matrix_row_name <-  paste("tech", 1:tech_num, sep = " ")
rownames(species_tech_matrix) <- matrix_row_name
```

```{r}
# print the catchability table 
matrix_table = kbl(species_tech_matrix, caption = "Catchability Matrix") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
matrix_table
```

We will evaluate this simple model under a linear and a exponential cost.

### Maximize Profit 

Since we are doing optimization year by year, let's see how the first year goes. 
<br>

##### **Object function**

$$
f(E) = E_1(q_{11}p_1X0_1+q_{21}p_2X0_2+q_{31}p_3X0_3) \\
+ E_2(q_{12}p_1X0_1+q_{22}p_2X0_2+q_{32}p_3X0_3) \\
+ E_3(q_{13}p_1X0_1+q_{23}p_2X0_2+q_{33}p_3X0_3) \\
- \beta_1E_1^2 - \beta_2E_2^2 - \beta_3E_3^2
$$

s.t.:
$$
q_{11}p_1X0_1E_1+q_{21}p_2X0_2E_1 + q_{12}p_1X0_1E_2+q_{22}p_2X0_2E_2 + \\
+ q_{13}p_1X0_1E_3+q_{23}p_2X0_2E_3 - Q_1 = 0 \\
$$

and 

$$
q_{31}p_3X0_3E_1 + q_{32}p_3X0_3E_2 + q_{33}p_3X0_3E_3 - Q_2 = 0
$$

<br>

#### **Lagrange maximization**
$$
L(E, \lambda) = f(E)  \\
+\lambda_1(q_{11}X0_1E_1+q_{21}X0_2E_1 + q_{12}X0_1E_2+q_{22}X0_2E_2 + \\
+ q_{13}X0_1E_3+q_{23}X0_2E_3 - Q_1) \\
+\lambda_2(q_{31}X0_3E_1 + q_{32}X0_3E_2 + q_{33}X0_3E_3 - Q_2) 
$$
**Lagrange Multiplier:**
<br>

$$
\begin{cases}
{\partial L \over \partial E_1} = q_{11}p_1X0_1+q_{21}p_2X0_2+q_{31}p_3X0_3- 2\beta_1E_1+\lambda_1(q_{11}X0_1+q_{21}X0_2) \\ 
+ \lambda_2(q_{31}X0_3) =0\\
{\partial L \over \partial E_2} = q_{12}p_1X0_1+q_{22}p_2X0_2+q_{32}p_3X0_3- 2\beta_2E_2+\lambda_1(q_{12}X0_1+q_{22}X0_2) + \\
+\lambda_2(q_{32}X0_3)=0\\
{\partial L \over \partial E_3} = q_{13}p_1X0_1+q_{23}p_2X0_2+q_{33}p_3X0_3- 2\beta_3E_3+\lambda_1(q_{13}X0_1+q_{23}X0_2) \\
+\lambda_2(q_{33}X0_3)=0\\
{\partial L \over \partial \lambda_1} = q_{11}X0_1E_1+q_{21}X0_2E_1 + q_{12}X0_1E_2+q_{22}X0_2E_2 + \\
+ q_{13}X0_1E_3+q_{23}X0_2E_3 - Q_1 \\
{\partial L \over \partial \lambda_2} = q_{31}X0_3E_1 + q_{32}X0_3E_2 + q_{33}X0_3E_3 - Q_2
\end{cases}
$$
<br>

